Emergence of the Southeast Asian islands as a driver for Neogene cooling

### 2020-04-13 Manuscript/Supplementary_Information.tex
Updates from Overleaf

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Figures/r2_cross_plot.pdf}
    \caption{Modeled vs. data-constrained \COtwo consumption in watersheds around the world. \textbf{A)} Each point represents a single watershed, and the y-value of the point shows the mean value of the 5,381 parameter combinations that produce individual watershed \COtwo consumption fluxes that approximate those estimated in the literature for the present-day (i.e. the orange points in Figure \ref{fig:W_vs_r2}). Whiskers extend to the minimum and maximum modeled watershed \COtwo consumption fluxes for the 5,381 parameters combinations. The red dashed line is the 1:1 line, the blue dashed line is the 2:1 line, and the cyan dashed lines are the 5:1 and 10:1 lines. \textbf{B)} Same as A, but only showing the parameter combination that produced that highest $r^{2}$. The chemical weathering and regolith thickness maps of this parameter combination are shown in Figure \ref{fig:weathering_regolith_maps}.}
    \label{fig:r2_cross_plot}
\end{figure}

@@

Within the equations that govern the chemical weathering rate in GEOCLIM, we identify the less constrained parameters: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$; Equation 9), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$; Equation 9), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$; Equation 4), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$; Equation 6). Furthermore, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. We therefore allow these parameters to vary within reasonable bounds during the calibration stage of GEOCLIM. In total, we test 78,000 unique parameter combinations (Fig. \ref{fig:r2_cross_plot}; Table \ref{tab:parameter_combinations}).

@@

The majority of the original 93,600 parameter combinations produce \COtwo consumption maps with poor fits to the measured watershed data (Fig. \ref{fig:W_vs_r2}). Given that the coefficient of determination ($r^{2}$) is calculated using Equation \ref{eq:10} rather than fitting a linear model, many of the combinations associated with particularly poor fits result in negative $r^{2}$ values (Fig. \ref{fig:W_vs_r2}). However, given the right permutation of parameters, GEOCLIM produces \COtwo consumption maps that fit the measured watershed data reasonably well. We therefore eliminate all parameter combinations that produce a $r^{2}\leq0.4$, which leaves 5,381 unique parameter combinations (Figs. \ref{fig:W_vs_r2} and \ref{fig:r2_cross_plot}).

Global CO$_{2}$ consumption calculated from these 5,381 parameter combinations ranges from 2.9$\times10^{12}$~mol/yr to 7.7$\times10^{12}$~mol/yr, with a mean of 5.7$\times10^{12}$~mol/yr. These estimates fall within the range of those independently estimated in the literature for the present-day: the full range of estimates of the present-day non-anthropogenic global CO$_{2}$ emission rate compiled in \citet{Gerlach2011a} is 3.0--10.0$\times10^{12}$~mol/yr, with the preferred range of those estimates being 3.4--5.9$\times10^{12}$~mol/yr (Fig. \ref{fig:W_vs_r2}B).

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Figures/scenario_pCO2_all.pdf}
    \caption{Steady-state \pCOtwo estimates from GEOCLIM for the various scenarios discussed in the text. For each of the 13 scenarios, each point represents an estimate from one of the 5,381 unique parameter combinations that resulted in reasonable total global \COtwo consumption and most closely matched estimates of present-day \COtwo consumption in 80 watersheds around the world (see SI). The box encloses the middle 50\% of the \pCOtwo estimates (i.e. the interquartile range), and the notch represents the median with its 95\% confidence interval. The whiskers extend to the 2.5 and 97.5 percentile values. This figure is identical to Figure 2 in the main text, except for the addition of the scenarios used to test the sensitivity of the results to the inclusion of the Sunda Shelf and the removal of the Greenland ice sheet.}
    \label{fig:scenario_pCO2_all}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Figures/r2_cross_plot.pdf}
    \caption{Modeled vs. data-constrained \COtwo consumption in watersheds around the world. \textbf{A)} Each point represents a single watershed, and the y-value of the point shows the mean value of the 573 parameter combinations that produce individual watershed \COtwo consumption fluxes that approximate those estimated in the literature for the present-day (i.e. the orange points in Figure \ref{fig:W_vs_r2}). Whiskers extend to the minimum and maximum modeled watershed \COtwo consumption fluxes for the 573 parameters combinations. Watersheds within the compilation of \citet{Gaillardet1999a} that are in the SEAI (Fly, Kikori, Purari, and Sepik watersheds, all in New Guinea) are indicated in green. \textbf{B)} Same as A, but only showing the parameter combination that produced that highest $r^{2}$. The chemical weathering and regolith thickness maps of this parameter combination are shown in Figure \ref{fig:weathering_regolith_maps}.}
    \label{fig:r2_cross_plot}
\end{figure}

@@

Within the equations that govern the chemical weathering rate in GEOCLIM, we identify the less constrained parameters: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$; Equation 9), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$; Equation 9), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$; Equation 4), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$; Equation 6). Furthermore, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. We therefore allow these parameters to vary within reasonable bounds during the calibration stage of GEOCLIM. In total, we test 93,600 unique parameter combinations (Fig. \ref{fig:r2_cross_plot}; Table \ref{tab:parameter_combinations}).

@@

The majority of the original 93,600 parameter combinations produce \COtwo consumption maps with poor fits to the measured watershed data (Fig. \ref{fig:W_vs_r2}). Given that the coefficient of determination ($r^{2}$) is calculated using Equation \ref{eq:10} rather than fitting a linear model, many of the combinations associated with particularly poor fits result in negative $r^{2}$ values (Fig. \ref{fig:W_vs_r2}). However, given the right permutation of parameters, GEOCLIM produces \COtwo consumption maps that fit the measured watershed data reasonably well. We therefore eliminate all parameter combinations that produce a $r^{2}\leq0.5$, which leaves 573 unique parameter combinations (Figs. \ref{fig:W_vs_r2} and \ref{fig:r2_cross_plot}).

Global CO$_{2}$ consumption calculated from these 573 parameter combinations ranges from 3.7$\times10^{12}$~mol/yr to 6.3$\times10^{12}$~mol/yr, with a mean of 5.2$\times10^{12}$~mol/yr. These estimates fall within the range of those independently estimated in the literature for the present-day: the full range of estimates of the present-day non-anthropogenic global CO$_{2}$ emission rate compiled in \citet{Gerlach2011a} is 3.0--10.0$\times10^{12}$~mol/yr, with the preferred range of those estimates being 3.4--5.9$\times10^{12}$~mol/yr (Fig. \ref{fig:W_vs_r2}B).

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Figures/scenario_pCO2_all.pdf}
    \caption{Steady-state \pCOtwo estimates from GEOCLIM for the various scenarios discussed in the text. For each of the 13 scenarios, each point represents an estimate from one of the 573 unique parameter combinations that resulted in reasonable total global \COtwo consumption and most closely matched estimates of present-day \COtwo consumption in 80 watersheds around the world. The box encloses the middle 50\% of the \pCOtwo estimates (i.e. the interquartile range), and the notch represents the median with its 95\% confidence interval. The whiskers extend to the 2.5 and 97.5 percentile values. This figure is identical to Figure 2 in the main text, except for the addition of the scenarios used to test the sensitivity of the results to the inclusion of the Sunda Shelf and the removal of the Greenland ice sheet.}
    \label{fig:scenario_pCO2_all}
\end{figure}
